%  article.tex (Version 3.3, released 19 January 2008)
%  Article to demonstrate format for SPIE Proceedings
%  Special instructions are included in this file after the
%  symbol %>>>>
%  Numerous commands are commented out, but included to show how
%  to effect various options, e.g., to print page numbers, etc.
%  This LaTeX source file is composed for LaTeX2e.

%  The following commands have been added in the SPIE class 
%  file (spie.cls) and will not be understood in other classes:
%  \supit{}, \authorinfo{}, \skiplinehalf, \keywords{}
%  The bibliography style file is called spiebib.bst, 
%  which replaces the standard style unstr.bst.  

\documentclass[letter]{spie}  %>>> use for US letter paper
%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
%% \addtolength{\voffset}{9mm}   %>>> moves text field down
%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 

%% Latex documents that need direct input
\input{latex/filesystem/package.tex}        % contains the latex packages
\input{content/00_frontmatter/frontmatter.tex}             % contains the Title and Autor info
\input{latex/filesystem/fileSetup.tex}      % contains package and variables init.
\input{content/acronym_definition.tex}      % contains the acronims 

%% Select inputing only one part of the document
%\includeonly{content/intro/intro}   % the file wihtout .tex
%\includeonly{content/other/other_content}
 
\begin{document} 
\maketitle 

\begin{abstract}
Prostate cancer has been reported as the second most frequently diagnosed men cancers in the world. In the last decades, new imaging techniques based on MRI have been developed in order to improve the diagnosis task of radiologists. In practise, diagnosis can be affected by multiple factors reducing the chance to detect potential lesions. Computer-aided detection and computer-aided diagnosis have been designed to answer to these needs and provide help to radiologists in their daily duties. In this study, we proposed an automatic method to detect prostate cancer from a per voxel manner using 3T multi-parametric MRI and a gradient boosting classifier. The best performances are obtained using all multi-parametric information as well as zonal information. The sensitivity and specificity obtained are 86.9\% and 84.6\%, respectively.
\end{abstract}

\keywords{Gradient boosting, multi-parametric MRI, prostate cancer, computer-aided diagnosis}

%% Incldue the content without .tex extension
\input{content/01_introduction/introduction}   % the file wihtout .tex
\input{content/02_methodology/methodology}
\input{content/03_results/results}
%\input{content/04_discussion/discussion}
\input{content/05_conclusion/conclusion}

\acknowledgments     %>>>> equivalent to \section*{ACKNOWLEDGMENTS}       

Guillaume Lema\^itre was supported by the Generalitat de Catalunya (grant nb. FI-DGR2012) and partly by the Mediterranean Office for Youth (grant nb. 2011/018/06). We would like also to thank the Clinica Girona (Catalunya,
Espanya) and the Centre Hospitalier of Dijon (France) for providing the MRI images used in this research.


\input{content/06_authorship/authorship}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% References %%%%%

\bibliography{./content/literature_review}   %>>>> bibliography data in report.bib
\bibliographystyle{spiebib}   %>>>> makes bibtex use spiebib.bst

\end{document} 
